---
title: "New Paretho Front Calculations - January 2026"
output:
  html_document:
    df_print: paged
---

This is a small notebook describing the evaluation of the new and cool methods developed by Arjun Chandrasekhar - but visualized / summarized by Magda Julkowska - so that the data will be ready for GWAS:

# data import

```{r}
data <- read.csv("best_of_best.csv")
meta <- read.csv("metadata.csv")
data
meta 
```

```{r}
meta$arbor.name2 <- paste(meta$genotype,"_",meta$replicate,"_",meta$condition,"_day",meta$day, sep="")
meta$arbor.name2 <- gsub(" ", "", meta$arbor.name2)
meta$arbor.name <- gsub(" ", "", meta$arbor.name)
meta$arbor.name %in% meta$arbor.name2
```


OK - let's get the natural diversity panel out of the data:

```{r}
unique(meta$experiment)

meta_GWAS <- c("PimpiBig1", "PimpiBig2", "PimpiBig3", "PimpiBig4", "PimpiBig5", "PimpiBig6")
meta_GWAS2 <- subset(meta, meta$experiment %in% meta_GWAS)
data$arbor.name %in% meta_GWAS2$arbor.name

data2 <- merge(data, meta_GWAS2, by = c("arbor.name"))
data2
```

OK - now let's summarize this so we have only one value for each genotype / condition:

```{r}
GWAS_means <- aggregate(
  cbind(optimal.G, optimal.alpha, optimal.pt.distance) ~ genotype + condition,
  data = data2,
  FUN = function(x) mean(x, na.rm = TRUE)
)
GWAS_means
```

OK - let's reshape this dataframe a little bit:

```{r}
unique(GWAS_means$condition)
GWAS_means$condition <- gsub(" ", "", GWAS_means$condition)
GWAS_means$condition <- gsub("s", "S", GWAS_means$condition)
GWAS_means_C <- subset(GWAS_means, GWAS_means$condition == "C")
GWAS_means_S <- subset(GWAS_means, GWAS_means$condition == "S")

colnames(GWAS_means_C)[3] <- "optimal.G.C"
colnames(GWAS_means_C)[4] <- "optimal.alpha.C"
colnames(GWAS_means_C)[5] <- "optimal.pt.dist.C"

colnames(GWAS_means_S)[3] <- "optimal.G.S"
colnames(GWAS_means_S)[4] <- "optimal.alpha.S"
colnames(GWAS_means_S)[5] <- "optimal.pt.dist.S"

GWAS_means_C <- GWAS_means_C[,c(1,3:5)]
GWAS_means_S <- GWAS_means_S[,c(1,3:5)]

GWAS <- merge(GWAS_means_C, GWAS_means_S, by = c("genotype"), all = T)
GWAS
```
ok - now let's save this file as GWAS_ready:

```{r}
write.csv(GWAS, "GWAS_ready.csv", row.names = F)
```

Cool - now let's have a look at how the values behave within one genotype under control vs salt stress:

```{r}
library(ggplot2)
library(ggsci)
library(ggpubr)
library(plotly)

pdf("Correlation_Alpha_Control_vs_Salt.pdf")
plot(
ggscatter(GWAS, x = "optimal.alpha.C", y = "optimal.alpha.S",
          add = "reg.line",                                 # Add regression line
          conf.int = TRUE,                                  # Add confidence interval
          add.params = list(color = "blue",
                            fill = "lightgray")
          )+
  stat_cor(method = "pearson", label.x = 0.03, label.y = 0.930)  # Add correlation coefficient
)
dev.off()
```

```{r}
pdf("Correlation_G_Control_vs_Salt.pdf")
plot(
ggscatter(GWAS, x = "optimal.G.C", y = "optimal.G.S",
          add = "reg.line",                                 # Add regression line
          conf.int = TRUE,                                  # Add confidence interval
          add.params = list(color = "blue",
                            fill = "lightgray")
          )+
  stat_cor(method = "pearson", label.x = -0.4, label.y = 1)  # Add correlation coefficient
)
dev.off()
```

```{r}
pdf("Correlation_dist_Control_vs_Salt.pdf")
plot(
ggscatter(GWAS, x = "optimal.pt.dist.C", y = "optimal.pt.dist.S",
          add = "reg.line",                                 # Add regression line
          conf.int = TRUE,                                  # Add confidence interval
          add.params = list(color = "blue",
                            fill = "lightgray")
          )+
  stat_cor(method = "pearson", label.x = -0.4, label.y = 1500)  # Add correlation coefficient
)
dev.off()
```

ok - now let's see how it compares with the ideotypes scored by hand:

```{r}
topology <- read.csv("manual-scoring-last-day.csv")
data2
topology

topology2 <- topology[,c(1:2,5)]

data3 <- merge(topology2, data2, by = c("experiment", "Picture.."))
data3
```
OK - so now let's see if we have significant differences in any of the newly calculated traits per condition and topology. First - lets rename the ideotype for topology tho:

```{r}
colnames(data3)[3] <- "topology"
unique(data3$condition)
data3$condition <- gsub(" ", "", data3$condition)
data3$condition <- gsub("s", "S", data3$condition)
data3$topology <- gsub("DT", "dT", data3$topology)
data3$topology <- gsub("CT", "C", data3$topology)
topology_ok <- c("C", "T", "dT", "B")
data4 <- subset(data3, data3$topology %in% topology_ok)

G_overall <- ggerrorplot(data4, x = "topology", y = "optimal.G", color = "topology", fill = "topology", facet = c("condition"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 2,
                          xlab="topology", ylab= "Optimal G", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "anova", label.y = 3) #+ stat_pvalue_manual(test, label = "Tukey", y.position = 25) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```


Interesting - let's add some Tukey comparison per each population:

```{r}
library(multcompView)
C <- subset(data4, data4$condition == "C")
Output <- TukeyHSD(aov(optimal.G ~ topology, data = C))
P9 = Output$topology[,'p adj']
stat.test<- multcompLetters(P9)
test <- as.data.frame(stat.test$Letters)
test$group1 <- rownames(test)
test$group2 <- rownames(test)
colnames(test)[1] <- "Tukey"
test$topology <- test$group1
test$condition <- "C"
test_all <- test


S <- subset(data4, data4$condition == "S")
Output <- TukeyHSD(aov(optimal.G ~ topology, data = S))
P9 = Output$topology[,'p adj']
stat.test<- multcompLetters(P9)
test <- as.data.frame(stat.test$Letters)
test$group1 <- rownames(test)
test$group2 <- rownames(test)
colnames(test)[1] <- "Tukey"
test$topology <- test$group1
test$condition <- "S"
test_all <- rbind(test, test_all)
test_all
```

```{r}
G_overall <- ggerrorplot(data4, x = "topology", y = "optimal.G", color = "topology", fill = "topology", facet = c("condition"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 2,
                          xlab="topology", ylab= "Optimal G", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "anova", label.y = 3) + stat_pvalue_manual(test_all, label = "Tukey", y.position = 2.5) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```
```{r}
pdf("Topology_of_OptimalG.pdf")
plot(G_overall)
dev.off()
```

```{r}
G_overall <- ggerrorplot(data4, x = "topology", y = "optimal.alpha", color = "topology", fill = "topology", facet = c("condition"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 2,
                          xlab="topology", ylab= "Optimal alpha", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "anova", label.y = 1.2) #+ stat_pvalue_manual(test, label = "Tukey", y.position = 25) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```


Interesting - let's add some Tukey comparison per each population:

```{r}
library(multcompView)
C <- subset(data4, data4$condition == "C")
Output <- TukeyHSD(aov(optimal.alpha ~ topology, data = C))
P9 = Output$topology[,'p adj']
stat.test<- multcompLetters(P9)
test <- as.data.frame(stat.test$Letters)
test$group1 <- rownames(test)
test$group2 <- rownames(test)
colnames(test)[1] <- "Tukey"
test$topology <- test$group1
test$condition <- "C"
test_all <- test


S <- subset(data4, data4$condition == "S")
Output <- TukeyHSD(aov(optimal.alpha ~ topology, data = S))
P9 = Output$topology[,'p adj']
stat.test<- multcompLetters(P9)
test <- as.data.frame(stat.test$Letters)
test$group1 <- rownames(test)
test$group2 <- rownames(test)
colnames(test)[1] <- "Tukey"
test$topology <- test$group1
test$condition <- "S"
test_all <- rbind(test, test_all)
test_all
```

```{r}
G_overall <- ggerrorplot(data4, x = "topology", y = "optimal.alpha", color = "topology", fill = "topology", facet = c("condition"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 2,
                          xlab="topology", ylab= "Optimal alpha", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "anova", label.y = 1.2) + stat_pvalue_manual(test_all, label = "Tukey", y.position = 1.1) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```
```{r}
pdf("Topology_of_OptimalAlpha.pdf")
plot(G_overall)
dev.off()
```

```{r}
G_overall <- ggerrorplot(data4, x = "topology", y = "optimal.pt.distance", color = "topology", fill = "topology", facet = c("condition"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 2,
                          xlab="topology", ylab= "Optimal pt distance", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "anova", label.y = 6000) #+ stat_pvalue_manual(test, label = "Tukey", y.position = 25) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```


Interesting - let's add some Tukey comparison per each population:

```{r}
library(multcompView)
C <- subset(data4, data4$condition == "C")
Output <- TukeyHSD(aov(optimal.pt.distance ~ topology, data = C))
P9 = Output$topology[,'p adj']
stat.test<- multcompLetters(P9)
test <- as.data.frame(stat.test$Letters)
test$group1 <- rownames(test)
test$group2 <- rownames(test)
colnames(test)[1] <- "Tukey"
test$topology <- test$group1
test$condition <- "C"
test_all <- test


S <- subset(data4, data4$condition == "S")
Output <- TukeyHSD(aov(optimal.pt.distance ~ topology, data = S))
P9 = Output$topology[,'p adj']
stat.test<- multcompLetters(P9)
test <- as.data.frame(stat.test$Letters)
test$group1 <- rownames(test)
test$group2 <- rownames(test)
colnames(test)[1] <- "Tukey"
test$topology <- test$group1
test$condition <- "S"
test_all <- rbind(test, test_all)
test_all
```

```{r}
G_overall <- ggerrorplot(data4, x = "topology", y = "optimal.pt.distance", color = "topology", fill = "topology", facet = c("condition"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 2,
                          xlab="topology", ylab= "Optimal pt distance", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "anova", label.y = 6000) + stat_pvalue_manual(test_all, label = "Tukey", y.position = 5500) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```
```{r}
pdf("Topology_of_OptimalPtDistance.pdf")
plot(G_overall)
dev.off()
```


Hmmm - this is all good and dandy - but how do I compare the variance for G :

```{r}
G_overall <- ggerrorplot(data4, x = "condition", y = "optimal.G", color = "condition", fill = "condition", facet = c("topology"),
                          desc_stat = "mean_sd", add = "jitter", ncol = 4,
                          xlab="condition", ylab= "Optimal G", add.params = list(color = "darkgray")) + scale_color_d3("category10") 
G_overall <- G_overall + stat_compare_means(method = "", label.y = 3) 
G_overall <- G_overall + rremove("legend") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
G_overall
```
```{r}
library(dplyr)
library(purrr)
library(broom)
library(ggplot2)

# df has: topology, condition (2 levels), optimal.G
vt <- data4 %>%
  group_by(topology) %>%
  summarise(
    p = tryCatch(var.test(optimal.G ~ condition, data = cur_data())$p.value,
                 error = function(e) NA_real_),
    .groups = "drop"
  ) %>%
  mutate(label = paste0("F-test p = ", signif(p, 3)))

# pick an annotation position per facet (top-left-ish)
pos <- data4 %>%
  group_by(topology) %>%
  summarise(
    x = 1,  # assumes condition is on x and has at least 2 levels
    y = max(optimal.G, na.rm = TRUE),
    .groups = "drop"
  )

ann <- left_join(vt, pos, by = "topology")
ann

ggplot(data4, aes(x = condition, y = optimal.G)) +
  geom_boxplot(outlier.alpha = 0.5) +
  facet_wrap(~ topology, scales = "free_y", ncol = 4) +
  geom_text(
    data = ann,
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    hjust = 0, vjust = 1
  )

p <- ggerrorplot(data4, x = "condition", y = "optimal.G", color = "condition", fill = "condition", facet.by = c("topology"),
                 desc_stat = "mean_sd", add = "jitter", ncol = 4, xlab="condition", ylab= "Optimal G", 
                 add.params = list(color = "darkgray")) + scale_color_d3("category10")
p <- p +geom_text(data = ann, aes(x = x, y = y, label = label), inherit.aes = FALSE, hjust = 0, vjust = 1, size = 3)
p
```
```{r}
pdf("G_over_Treatment_per_Topology.pdf")
plot(p)
dev.off()
```

